Blame and Coercion: Together Again for the Second Time

### 2019-10-11 paper.tex
new sections

@@

@@

\begin{theorem}[\lazyD{} Hyper-coercion is a proper cast representation]
	See appendix.
\end{theorem}

\begin{corollary}[\lazyD{} hyper-coercion is correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	e \Downarrow_{D,B} o \; \text{if and only if} \; 
	e \Downarrow_{D,P(H)} o
	\]
\end{corollary}

>>>>

\section{Space-efficient CEK Abstract Machine}

[move the definition of the generic machine here -Jeremy]

@@

\subsection{Correctness of \lazyD{} Hyper-coercions}

@@

\begin{lemma}[\lazyD{} Hyper-coercion is a proper cast representation]
	See appendix.
\end{lemma}

\begin{theorem}[\lazyD{} hyper-coercion is correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	e \Downarrow_{D,B} o \; \text{if and only if} \; 
	e \Downarrow_{D,P(H)} o
	\]
\end{theorem}
